Somatosensory Response Changes During Illusory Finger Stretching

### 2024-05-14 manuscript.qmd
Fix and streamline of raw data download

if (processdata==1){
  for (subj in 1:48){
    if (!dir.exists('local/EEG Data/P',subj)){dir.create('local/EEG Data/P',subj)}
  }
}

if (processdata==1){
  for (subj in 1:48){
    if (!file.exists('local/EEG Data/P',subj,'/P',subj,'_block1_EEG.fdt')){
    osfproject <- osf_retrieve_node("xc8jq")
    osffiles <- osf_ls_files(osfproject)
    fid <- which(osffiles$name=='P',subj,'_block1_EEG.fdt')
    osf_download(osffiles[fid,], path='local/EEG Data/P',subj,progress=TRUE)
}
}
}

if (processdata==1){
  for (subj in 1:48){
    if (!file.exists('local/EEG Data/P',subj,'/P',subj,'_block1_EEG.set')){
    osfproject <- osf_retrieve_node("xc8jq")
    osffiles <- osf_ls_files(osfproject)
    fid <- which(osffiles$name=='P',subj,'_block1_EEG.set')
    osf_download(osffiles[fid,], path='local/EEG Data/P',subj,progress=TRUE)
}
}
}

>>>>

if (processdata==1){
    for (subj in 1:48){
    if (!dir.exists('local/EEG Data/P',subj)){dir.create('local/EEG Data/P',subj)}
  }
  osfproject <- osf_retrieve_node("xc8jq")
  osffiles <- osf_ls_files(osfproject)
  for (subj in 1:48){
    if (!file.exists('local/EEG Data/P',subj,'/P',subj,'_block1_EEG.fdt')){
    fid <- which(osffiles$name=='P',subj,'_block1_EEG.fdt')
    osf_download(osffiles[fid,], path=paste0('local/EEG Data/P',subj),progress=TRUE)
    }
    if (!file.exists('local/EEG Data/P',subj,'/P',subj,'_block1_EEG.set')){
    fid <- which(osffiles$name=='P',subj,'_block1_EEG.set')
    osf_download(osffiles[fid,], path=paste0('local/EEG Data/P',subj),progress=TRUE)
}}}
